Measurement Bias from Address Aliasing

### 2016-01-09 paper.tex
Shortened the end.
Remove redundant stuff from address space caption

% Virtual memory/randomization illustration
\begin{figure}
  \centering
  \begin{tikzpicture}[font=\footnotesize]
    % See page 453 in pgf manual
    \node [
      rectangle split, rectangle split parts=10, 
      rectangle split part fill={white, white, lightgray, white, lightgray, white, lightgray, white},
      draw, anchor=center, text width=2cm
    ] (m) {
        \nodepart{one}
          environment
        \nodepart{two}
          stack
        \nodepart{four}
          mmap area
        \nodepart{six}
          heap
        \nodepart{eight}
          bss
        \nodepart{nine}
          data
        \nodepart{ten}
          text
      };
    \draw [decorate, decoration={brace, amplitude=5pt}] (m.south west) -- (m.seven split west) 
      node [black, midway, xshift=-1.5cm, text width=2.0cm] 
        { Program code and static data } ;
    \node[right] at (m.north east)
      { \scriptsize{0x7fff'ffffffff} } ;
    \node[right] at (m.south east)
      { \scriptsize{0x400000} } ;
  \end{tikzpicture}
  \caption{Memory execution context, assuming a 64-bit process running on a Linux system.
  Initial addresses of stack, heap and memory mapped files are often randomized for security reasons.
  The stack is also offset by environment variables and program arguments.
  Addresses of code and statically allocated data are allocated at compile time by the linker, and can be determined by inspecting the executable.}
  \label{fig:virtualmemory}
\end{figure}

>>>>

% Virtual memory/randomization illustration
\begin{figure}
  \centering
  \begin{tikzpicture}[font=\footnotesize]
    % See page 453 in pgf manual
    \node [
      rectangle split, rectangle split parts=10, 
      rectangle split part fill={white, white, lightgray, white, lightgray, white, lightgray, white},
      draw, anchor=center, text width=2cm
    ] (m) {
        \nodepart{one}
          environment
        \nodepart{two}
          stack
        \nodepart{four}
          mmap area
        \nodepart{six}
          heap
        \nodepart{eight}
          bss
        \nodepart{nine}
          data
        \nodepart{ten}
          text
      };
    \draw [decorate, decoration={brace, amplitude=5pt}] (m.south west) -- (m.seven split west) 
      node [black, midway, xshift=-1.5cm, text width=2.0cm] 
        { Program code and static data } ;
    \node[right] at (m.north east)
      { \scriptsize{0x7fff'ffffffff} } ;
    \node[right] at (m.south east)
      { \scriptsize{0x400000} } ;
  \end{tikzpicture}
  \caption{Memory execution context, assuming a 64-bit process running on a Linux system.}
  %Initial addresses of stack, heap and memory mapped files are often randomized for security reasons.
  %The stack is also offset by environment variables and program arguments.
  %Addresses of code and statically allocated data are allocated at compile time by the linker, and can be determined by inspecting the executable.}
  \label{fig:virtualmemory}
\end{figure}
